FINE SCALE REGISTRATION OF SIDEWALKS AND OTHER RIBBON-LIKE FEATURES FROM AERIAL IMAGERY

### 2018-07-27 Chapters/4.Expect_results/Results.tex
editing new figure and remove bad image

Figure \ref{fig:penalty} shows our algorithm managed to separate the driveway and sidewalk under the same feature as penalty increase. So we could apply the dynamic programming solution to locate the precise boundaries of given ribbon image. The penalty control improved our performance significantly. Because of this, our approach could predict the sidewalk under the tree shadow and other shadows or obstacles, which bring us more accurate result compare to other methods.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{Figures/penalty.png}
    \caption[Penalty Process]{Comparison with penalty change, we tested a variety of variables to decide which variable had best performance for width control. With the penalty increased at a reasonable amount, our algorithm decided not to recognize a driveway as sidewalk walk, in order to keep the sidewalk width consistent, even though they are the same texture.}
    \label{fig:penalty}
\end{figure}
As shown in figure \ref{fig:sample_result2}, after we generate the result on ribbon image, just need to simply covert the ribbon image back to its original shape by reverse the method that generates the ribbon image.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{Figures/changes_on_recall.png}
    \caption[Parameters Evaluation]{Detail comparison on $c_{bend}$, $c_{shrink}$ and $c_{expand}$. Where red line represent $c_{bend}$, green line represent $c_{shrink}$ and blue line represent $c_{expand}$. We generate these based on equations from Recall (6.2), Precision (6.1), F1 (6.3) and Intersection over Union.}
    \label{fig:change_on_recall}
\end{figure}

>>>>

Figure \ref{fig:penalty} shows our algorithm managed to separate the driveway and sidewalk under the same feature as penalty increase. So we could apply the dynamic programming solution to locate the precise boundaries of given ribbon image. The penalty control improved our performance significantly. Because of this, our approach could predict the sidewalk under the tree shadow and other shadows or obstacles, which bring us more accurate result compare to other methods.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{Figures/penalty.png}
    \caption[Penalty Process]{Comparison with penalty change, we tested a variety of variables to decide which variable had best performance for width control. With the penalty increased at a reasonable amount, our algorithm decided not to recognize a driveway as sidewalk walk, in order to keep the sidewalk width consistent, even though they are the same texture.}
    \label{fig:penalty}
\end{figure}

As shown in figure \ref{fig:sample_result2}, after we generate the result on ribbon image, just need to simply covert the ribbon image back to its original shape by reverse the method that generates the ribbon image.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.85\textwidth]{Figures/prf.png}
    \caption[Parameters Evaluation]{Detail comparison on $c_{bend}$, $c_{shrink}$ and $c_{expand}$. Where red line represent Recall, green line represent Precision and blue line represent F1. We generate these based on equations from Recall (6.2), Precision (6.1), F1 (6.3).}
    \label{fig:change_on_recall}
\end{figure}
